

%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Sudev A. C.
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{amsmath}
\hypersetup{
	bookmarks=true, 					%Enable pdf bookmarks
	pdfborder={0,0,0},					%Disable borders around links
	pdftitle={Sudev A. C.},			%Name of PDF document
	colorlinks={true},					%Enable colored links
	linkcolor=black,						%Internal link color
	citecolor=black,						%Citation link color
	filecolor=black,						%File link color
	urlcolor=black						%URL link color
}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Sudev A. C.}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    
        
    Ambadi House   \hfill \textit{mobile:} \hspace{9mm} 		+91-8089442513 \\ 
    Ponnani South P. O.	\hfill \textit{webpage:}\hspace{14mm}\href{http://sudev.github.io}{sudev.github.io}\\
    Malappuram \hfill 	\textit{e-mail:} \hspace{3.6mm}\href{mailto:sudevdev@gmail.com}{sudevdev@gmail.com}     \\
    Kerala - 679586
			
        \vspace{-2.5mm}
        
        \vspace{3mm}
%
					
%				 \\	  						
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Areas of\\Interest}

   GNU/Linux, Cloud Computing, Operating Systems \&  Data Mining.
\vspace{3mm}


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{National Institute of Technology Calicut} \hfill \textit{Calicut, Kerala, India} \vspace{1mm}\\\vspace{1mm}%
    \textsl{B.Tech, Computer Science and Engineering} \hfill \textit{ July 2010 -- May 2014}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item[--] Cumulative GPA: 7.28/10 
        \item[--] \textit{Relevant Courses}: Data Structures \& Algorithms, Design \& Analysis of Algorithms, Theory
of Computation, Computer Networks, Discrete Computational Structures, Operating Systems, 
Compilers, Number Theory and Cryptography, Computer Security, Natural Language Processing.
    \end{list2}\vspace{-1.5mm}
    
 \vspace{3mm}

    %__________________________________________________________________________________________________________________

    % Projects
    \section{\mysidestyle Work Experience}


    \textbf{EY Innovation Center } 				\hfill  Trivandrum, Kerala \\
      \textit{Position: Associate } 			\hfill \textit{June 2014 -- present}
  

Data Harvester				 				\hfill \textit{Jan 2015 -- present} \\
\textit{Summary} : Apache Spark application to harvest valuable information from public filings. \\
      \textit{Technologies} : Apache Spark, Python/Java, MongoDB\\
\textit{Responsibilities} : 
     	 	\begin{list2}
\item[--]Implement Apache Spark application to process real-time stream of financial filings harnessing 
 in-memory processing capabilities of Apache Spark on Hadoop/YARN.
	\item[--] Setting up Linux cluster to run Apache Spark on Hadoop-YARN environment.% and mongodb server for caching the results.
	\item[--] Implement prediction models for forecasting financials using harvested data.
	\end{list2}

    Market Trigger				 \hfill \textit{June 2014 -- Dec 2014} \\
\textit{Summary} : A cloud based application for triggers and insights relevant to EY's market.	 \\
      \textit{Technologies} : Python, R, Linux\\
      \textit{Responsibilities} : 
%Design and implement data mining techniques in Python and R to gain market triggers from social media and news/rss feeds. 
     	 	\begin{list2}
\item[--] Design and implement data mining techniques in Python and R to gain market triggers from
social media and news/rss feeds.	
	\item[--] Setting up Linux server environment in cloud to serve realtime push notifications.
	\end{list2}

	 
 \vspace{3mm}

    %__________________________________________________________________________________________________________________

    % Projects
    \section{\mysidestyle Projects}

   
	
	
    \textbf{Experiments with Minix 3 operating system } 				\hfill NIT Calicut \\
      \textit{Supervisor: Dr. K Muralikrishnan } 			\hfill \textit{August 2013 -- May 2014}\\
      \textit{Technologies: Minix 3 operating system, Minix File System, C }\\
    Implementation of immediate files in Virtual filesystem of Minix 3 operating system. Immediate files are small files accommodated in the inode itself instead of allocating a disk block. 

    \textbf{High Performance Computing \& Virtualization in the Cloud} 				\hfill NIT Calicut \\
      \textit{Supervisor: Dr. Vineeth Paleri } 			\hfill \textit{December 2012 -- January 2014}\\
      \textit{Technologies: Eucalyptus Cloud, Rocks Cluster, Shell Scripting, Linux Networking}\\
    Setting up a scalable private cloud in the campus using open source tools like Eucalyptus and Rocks,
capable of high performance computing and virtualization.  A cloud alternative for Computer Science
programming laboratory and provides IaaS for student community in campus.
	\vspace{2mm}%
%
%	   \textbf{Simple Integer Language (SIL) Compiler} 						\hfill NIT Calicut \\
%    \textit{Class Project, Compiler Design} 							\hfill \textit{August 2012 -- November 2012}\\
%	Engineered a compiler for a simple \& strongly typed language, SIL in C using tools like LEX and YACC.
%   \vspace{2mm}%
%   
%   
%   
%    
%    \textbf{Tux of War} 								\hfill NIT Calicut \\
%    \textit{Technical Event, Tathva 2011} 							\hfill \textit{August 2012 -- October 2012}\\
%    \textit{Technologies: Linux, Google App Engine} \\
%   Organized and prepared questions for a Linux know how and shell scripting event as part of Tathva ’12 (Technical Fest of NIT      Calicut).An online quiz was conducted using Google App engine, mocking a Linux terminal.
%      \vspace{2mm}%
      
      
%    \textbf{FOSSCell Website and Mirror} 						\hfill NIT Calicut \\
%    \textit{Technical Club, NIT Calicut} 							\hfill \textit{May 2011 -- June 2011}\\
%    \textit{Technologies: Drupal CMS, HTML/CSS, Fedora Linux Server} \\
%	A new website for Free and Open Source Cell of NIT Calicut where members can share knowledge,
%thoughts and discuss about Free Software’s. A local Linux server was configured to host website
%along with a Fedora Mirror.
   

%    % Projects
%    \section{\mysidestyle Work Experience}
%
%   
%	
%	
%    \textbf{EY Innovation Center, EY GTH } 				\hfill  Trivandrum, Kerala \\
%      \textit{Position: Associate } 			\hfill \textit{June 2014 -- present}\\
%      \textit{Technologies: R, Python }\\
%	 
\pagebreak
   \section{\mysidestyle Skills} 
    	\begin{list2}
	\item \textit{Programming}: C, Python, Shell Scripting, R, Java
	\item \textit{Distributed Computing/Cloud}: Apache Spark, Horton data platform, Eucalyptus	
	\item \textit{Web}: Drupal, HTML/CSS	
	\item \textit{Tools}: LEX, YACC, GIT, VIm
	
	% \item \textit{DBMS}: MySQL
	\item \textit{Platforms}: GNU/Linux, Windows
	\end{list2}


    %__________________________________________________________________________________________________________________
    %  Workshops Attended
    \section{\mysidestyle Workshops Attended} 
	FOSS.in \hfill \textit{Bangalore, November 2012}  \\%   
    Yahoo Open Hack India \hfill \textit{Bangalore, June 2012}    \\
    Cloud \& Linux by IBM \hfill \textit{NIT Calicut, April 2013}    \\

            


    %__________________________________________________________________________________________________________________
    %  Talks Given
    \section{\mysidestyle Workshops Taken} 
	Data mining and R programming \hfill \textit{EY Innovation Trivandrum, March 2015}    \\
	Introduction to Shell Scripting \hfill \textit{NIT Calicut, January 2014}    \\    	
	Introduction to GNU/Linux \hfill \textit{NIT Calicut, February 2013}    \\
		    			

    %__________________________________________________________________________________________________________________
    %  Responsibilities Held
    \section{\mysidestyle Responsibilities Held } 
	\begin{list2}
	\item[--] Organizer \& Web Developer at TEDxNITCalicut.
	\item[--] Lab Administrator (Biocomputing Research Laboratory) and HPC Cluster Administrator
	\item[--] Evangelist at FOSSCell NIT Calicut.	
	\item[--] Web Admin FOSSCell NIT Calicut \& Fedora Mirror NIT Calicut.
	\item[--] Member of core team of FOSSMeet 2011-2014.
	
	
	\end{list2}
%
%    %__________________________________________________________________________________________________________________
%    % Computer Skills
%    \section{\mysidestyle Skills} 
%    	\begin{list2}
%	\item \textit{Programming}: C, Python, Shell Scripting, R
%	\item \textit{Tools}: LEX, YACC, GIT, VIm
%	% \item \textit{CMS}: Drupal
%	% \item \textit{DBMS}: MySQL
%	\item \textit{Platforms}: GNU/Linux, Windows
%	\item \textit{Cloud}: Eucalyptus
%	\end{list2}
%



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

